\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\pdfgentounicode=1

% Section Formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Almoiz Khan} \\ \vspace{1pt}
    \small Hyderabad, India $|$ \href{mailto:almoiz907@gmail.com}{almoiz907@gmail.com} $|$ +91 9989538057 \\
    \href{https://almoizkhan.tech}{Portfolio} $|$
    \href{https://linkedin.com/in/almoiz-khan}{LinkedIn} $|$
    \href{https://github.com/moiz2405}{GitHub}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    Founding Engineer and Lead Developer at BharatNiti AI, owning end-to-end system design, development, deployment, and scaling of production systems. Strong focus on backend engineering, cloud infrastructure, DevOps, and cost-efficient system architecture.
  }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bachelor of Technology in Computer Science (Cyber Security)}{Nov 2022 -- May 2026}
    {Marri Laxman Reddy Institute of Technology and Management}{Hyderabad, India | CGPA: 9.27/10}
\resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Founding Engineer \& Lead Developer}{Dec 2025 -- Present}
    {BharatNiti AI}{Remote}
    \resumeItemListStart
      \resumeItem{Owning end-to-end system architecture, development, deployment, and production scalability across the platform.}
      \resumeItem{Leading frontend, backend, and infrastructure decisions with a focus on performance, security, and cost optimization.}
      \resumeItem{Collaborating with founders on technical strategy, product roadmap, and long-term scalability planning.}
    \resumeItemListEnd

  \resumeSubheading
    {Full Stack Developer Intern (Early Team Member)}{Sep 2025 -- Dec 2025}
    {BharatNiti AI}{Remote}
    \resumeItemListStart
      \resumeItem{Reduced cloud infrastructure costs by \textbf{~90\%}, cutting expenses from \textbf{\$300K/year to under \$20K/year} by migrating from managed cloud services to self-managed VMs and VPS.}
      \resumeItem{Decomposed a monolithic application into \textbf{microservices}, improving scalability, fault isolation, and deployment velocity.}
      \resumeItem{Optimized backend APIs and frontend data flow, reducing \textbf{40--50\% API calls} and significantly improving UI performance.}
      \resumeItem{Owned infrastructure end-to-end including servers, deployments, monitoring, and security using Next.js and FastAPI.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Craftable – No-Code Portfolio Builder} $|$ \emph{Next.js, TypeScript, Tailwind CSS}}{}
    \resumeItemListStart
      \resumeItem{Built a no-code portfolio platform with reusable components and drag-and-drop templates.}
      \resumeItem{Deployed on Vercel with CI/CD enabling rapid iteration and versioned releases.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Vision – AI Developer Assistant} $|$ \emph{Python, Agno, TTS/STT}}{}
    \resumeItemListStart
      \resumeItem{Built a developer assistant with TTS/STT integration achieving 95\%+ voice command accuracy.}
      \resumeItem{Improved developer productivity by 30\% through voice-driven automation and task execution.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \item
    \resumeItemListStart
      \resumeItem{\textbf{Cloud \& DevOps:} AWS (EC2, S3), Docker, Kubernetes, Terraform, VPS, Linux}
      \resumeItem{\textbf{Backend:} FastAPI, Node.js, PostgreSQL, MongoDB}
      \resumeItem{\textbf{Frontend:} Next.js, React.js, TypeScript}
      \resumeItem{\textbf{Languages:} JavaScript, TypeScript, Python, C++, Java}
      \resumeItem{\textbf{CI/CD Tools:} GitHub Actions, Jenkins, GitLab CI/CD}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\resumeSubHeadingListStart
  \item
    \resumeItemListStart
      \resumeItem{Finalist – Smart India Hackathon 2024 (led a 6-member team)}
      \resumeItem{Part of Intel® Unnati Smart Innovation Labs – AI/ML Cohort (May 2025)}
      \resumeItem{Top 9\% globally on LeetCode with 300+ solved problems}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeSubHeadingListStart
  \item
    \resumeItemListStart
      \resumeItem{Smart Interviews DSA Certification – Platinum Smart Coder (Top 2\%) – Mar 2025}
      \resumeItem{Postman API Fundamentals Student Expert – Nov 2024}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
